Meta-analysis of the Interoceptive Accuracy Scale

### 2024-02-26 analysis/study2.qmd
Update study2.qmd

vars_intero <- names(select(scores$sample1a, -Sample, -starts_with("CFA_"), -starts_with("EGA")))
# vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
# vars_cfa7 <- vars_cfa[vars_cfa != "CoughSneeze"]

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ, TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ, BPQ, MAIA, BPCS
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES
# names(df7b)  # MAIA, STAIT, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, TAS, ASI, BDI, IASV
# names(df8a)  # EDI, BPQ
# names(df8b)  # TAS,PHQ15, PHQ9
# names(df9)  # BFI, STQ, EQ, ECR, 
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10n)  # BDI, STAI, PHQ4
```

@@

data <- rbind(
  make_diff(df1a, vars_intero, component="Demographic"),
  make_diff(df1b, vars_intero, component="Demographic"),
  make_diff(df2, vars_intero, component="Demographic"),
  make_diff(df3, vars_intero, component="Demographic"),
  # make_diff(df4, vars_intero, component="Demographic"),
  # make_diff(df5, vars_intero, component="Demographic"),
  make_diff(df6, vars_intero, component="Demographic"),
  make_diff(df7a, vars_intero, component="Demographic"),
  make_diff(df7b, vars_intero, component="Demographic"),
  make_diff(df7c, vars_intero, component="Demographic"),
  make_diff(df8a, vars_intero, component="Demographic"),
  make_diff(df8b, vars_intero, component="Demographic"),
  make_diff(df9, vars_intero, component="Demographic"),
  make_diff(df10a, vars_intero, component="Demographic"),
  make_diff(df10b, vars_intero, component="Demographic")
) |>
  mutate(var_Correlate = "Gender (Male vs. Female)")
```

@@

data <- rbind(
  data,
  make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df1b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df2, vars_intero, with = "Age", component="Demographic"),
  make_cor(df3, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df4, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df5, vars_intero, with = "Age", component="Demographic"),
  make_cor(df6, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df9, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10b, vars_intero, with = "Age", component="Demographic")
)
```

@@

```{r}
# df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
# df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
names(df2)  # BPQ_R_Supra and _Sub?
names(df3)
names(df4)  # individual items 1-26
names(df7b)  # BPQ sum
names(df8a)  # individual items

data <- rbind(
  data,
  make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df2, vars_intero, with = "BPQ_R", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)")
)
```

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_AttentionRegulation", component="MAIA")  |>  -->
<!--     mutate(var_Correlate = "Attention Regulation"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_BodyListening", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Body Listening"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_EmotionalAwareness", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Emotional Awareness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotDistracting", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Not Distracting"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Noticing", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Noticing"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_NotWorrying", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Not Worrying"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_SelfRegulation", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Self Regulation"), -->
<!--   make_cor(df5a, vars_cfa7, with = "MAIA_Trusting", component="MAIA") |>  -->
<!--     mutate(var_Correlate = "Trusting") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- # names(df3)[str_detect(names(df3), "TAS")] -->
<!-- # names(df4b)[str_starts(names(df4b), "TAS")] -->

<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df3, vars_cfa, with = "TAS_IdentifyingFeelings", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
<!--   make_cor(df3, vars_cfa, with = "TAS_DescribingFeelings", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Describing Feelings"), -->
<!--   make_cor(df3, vars_cfa, with = "TAS_ExternallyOrientedThinking", component="Body") |>  -->
<!--     mutate(var_Correlate = "External Thinking"), -->
<!--   make_cor(df4b, vars_cfa, with = "TAS_DIF", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Identifying Feelings"), -->
<!--   make_cor(df4b, vars_cfa, with = "TAS_DDF", component="Body") |>  -->
<!--     mutate(var_Correlate = "Difficulties Describing Feelings") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Mood -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df4b, vars_cfa, with = "PHQ15_sum", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Somatic Concerns (PHQ-15)"), -->
<!--   make_cor(df4b, vars_cfa, with = "PHQ9_sum", component="Mood")|>  -->
<!--     mutate(var_Correlate = "Depression (PHQ-9)"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Depression", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Depression (PHQ-4)"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PHQ4_Anxiety", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Anxiety (PHQ-4)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5b, vars_cfa, with = "BDI2_Total", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Depression (BDI-II)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5b, vars_cfa, with = "STAI5_General", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Anxiety (STAI-5)") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "BPD", component="Mood") |>  -->
<!--     mutate(var_Correlate = "Boderline Personality") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Psychopathology -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Antagonism", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Antagonism"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Detachment", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Detachment"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Disinhibition", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Disinhibition"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_NegativeAffect", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Negative Affect"), -->
<!--   make_cor(df5a, vars_cfa7, with = "PID5_Psychoticism", component="Maladaptive") |>  -->
<!--     mutate(var_Correlate = "Psychoticism") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_ConstrictedAffect", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Constricted Affect"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Eccentric", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Eccentric"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_MagicalThinking", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Magical Thinking"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_NoCloseFriends", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "No Close Friends"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_OddSpeech", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Odd Speech"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Reference", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Reference"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_SocialAnxiety", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Social Anxiety"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_Suspiciousness", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Suspiciousness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "SPQ_UnusualPerceptions", component="Schizotypic") |>  -->
<!--     mutate(var_Correlate = "Unusual Perceptions") -->
<!-- ) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #  names(select(df5a, starts_with("ASQ"))) -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Imagination", component="Autistic") |>  -->
<!--     mutate(var_Correlate = "Imagination"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LackSocialSkills", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Lack of Social Skills"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_LowAttentionalSwitching", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Low Attentional Switching"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Patterns", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Patterns and Numbers"), -->
<!--   make_cor(df5a, vars_cfa7, with = "ASQ_Routine", component="Autistic") |> -->
<!--     mutate(var_Correlate = "Routines") -->
<!-- ) -->
<!-- ``` -->

<!-- ### Personality -->

<!-- ```{r} -->
<!-- data <- rbind( -->
<!--   data, -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Agreeableness", component="Personality") |>  -->
<!--     mutate(var_Correlate = "Agreeableness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Conscientiousness", component="Personality") |> -->
<!--     mutate(var_Correlate = "Conscientiousness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Neuroticism", component="Personality") |> -->
<!--     mutate(var_Correlate = "Neuroticism"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Openness", component="Personality") |> -->
<!--     mutate(var_Correlate = "Openness"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_Extraversion", component="Personality") |> -->
<!--     mutate(var_Correlate = "Extraversion"), -->
<!--   make_cor(df5a, vars_cfa7, with = "IPIP6_HonestyHumility", component="Personality") |> -->
<!--     mutate(var_Correlate = "Honesty-Humility") -->
<!-- ) -->
<!-- ``` -->

>>>>

vars_intero <- names(select(scores$sample1a, -Sample, -starts_with("CFA_"), -starts_with("EGA")))
# vars_cfa <- names(select(scores$sample1a, -Sample, -starts_with("EGA")))
# vars_intero <- vars_cfa[vars_cfa != "CoughSneeze"]

# names(df1a)
# names(df1b)
# names(df2)  # BPQ, BVAQ, MAIA, ICQ, TAS
# names(df3)  # TAS, BPQ
# names(df4)  # BAQ, BPQ, MAIA, BRS, PBCS
# names(df5)  
# names(df6)  # IATS, SSS, GAD, PHQ2
# names(df7a)  # MAIA, STAI, FFMQ, NEOFFI, CES (?)
# names(df7b)  # MAIA, STAI, BPQ, PHQ15, PHQ9
# names(df7c)  # TAS, BPQ, ASI, BDI, CI (?), IASV (?), IASP (?)
# names(df8a)  # EDI (eating disorder inventory?), BPQ
# names(df8b)  # TAS, PHQ15, PHQ9
# names(df9)  # BFI, STQ (?), EQ (?), ECR (?), TEAQ (?), UCLA (?), TACSEN (?)
# names(df10a)  # MAIA, PHQ4, PI, LIE, IPIP, PID, SPQ
# names(df10b)  # BDI, STAI, PHQ4
```

@@

rez_gender <- rbind(
  make_diff(df1a, vars_intero, component="Demographic"),
  make_diff(df1b, vars_intero, component="Demographic"),
  make_diff(df2, vars_intero, component="Demographic"),
  make_diff(df3, vars_intero, component="Demographic"),
  # make_diff(df4, vars_intero, component="Demographic"),
  # make_diff(df5, vars_intero, component="Demographic"),
  make_diff(df6, vars_intero, component="Demographic"),
  make_diff(df7a, vars_intero, component="Demographic"),
  make_diff(df7b, vars_intero, component="Demographic"),
  make_diff(df7c, vars_intero, component="Demographic"),
  make_diff(df8a, vars_intero, component="Demographic"),
  make_diff(df8b, vars_intero, component="Demographic"),
  make_diff(df9, vars_intero, component="Demographic"),
  make_diff(df10a, vars_intero, component="Demographic"),
  make_diff(df10b, vars_intero, component="Demographic")
) |>
  mutate(var_Correlate = "Gender (Male vs. Female)")

display_sig <- function(rez) {
  rez |> 
    arrange(var_Interoception, var_Correlate, desc(abs(r))) |> 
    mutate(CI = insight::format_ci(CI_low, CI_high, ci=CI)) |>
    select(Sample, var_Correlate, var_Interoception, r, CI, p) |>
    gt::gt() |> 
    gt::data_color(
      columns = r,
      rows = p < 0.5,
      method = "numeric",
      palette = c("blue", "red")
    ) |> 
    gt::fmt_number(decimals=3) |> 
    gt::opt_stylize() |> 
    gt::opt_interactive(use_compact_mode = TRUE) 
}

display_sig(rez_gender)
```

### Age

@@

rez_age <- rbind(
  make_cor(df1a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df1b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df2, vars_intero, with = "Age", component="Demographic"),
  make_cor(df3, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df4, vars_intero, with = "Age", component="Demographic"),
  # make_cor(df5, vars_intero, with = "Age", component="Demographic"),
  make_cor(df6, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df7c, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df8b, vars_intero, with = "Age", component="Demographic"),
  make_cor(df9, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10a, vars_intero, with = "Age", component="Demographic"),
  make_cor(df10b, vars_intero, with = "Age", component="Demographic")
)

display_sig(rez_age)
```

## Body

### MAIA

```{r}
# names(df2)[str_detect(names(df2), "MAIA")]  
# names(df4)[str_detect(names(df4), "MAIA")] 
# names(df7a)[str_detect(names(df7a), "MAIA")]  
# names(df7b)[str_detect(names(df7b), "maia")] 
# names(df10a)[str_detect(names(df10b), "MAIA")]

df4$MAIA_BL <- rowMeans(df4[grep("MAIA_BL", names(df4))])
df4$MAIA_TR <- rowMeans(df4[grep("MAIA_TR", names(df4))])
df4$MAIA_AR <- rowMeans(df4[grep("MAIA_AR", names(df4))])
df4$MAIA_SR <- rowMeans(df4[grep("MAIA_SR", names(df4))])
df4$MAIA_EA <- rowMeans(df4[grep("MAIA_EA", names(df4))])
df4$MAIA_NT <- rowMeans(df4[grep("MAIA_NT", names(df4))])

rez_maia <- rbind(
  make_cor(df2, vars_intero, with = "MAIA_AttentionReg", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df2, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df2, vars_intero, with = "MAIA_BodyTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),
  make_cor(df2, vars_intero, with = "MAIA_EmoAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df2, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df2, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df2, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df2, vars_intero, with = "MAIA_SelfReg", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  # df4
  make_cor(df4, vars_intero, with = "MAIA_BL", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df4, vars_intero, with = "MAIA_TR", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),
  make_cor(df4, vars_intero, with = "MAIA_AR", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df4, vars_intero, with = "MAIA_SR", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df4, vars_intero, with = "MAIA_EA", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df4, vars_intero, with = "MAIA_NT", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  # df7a
  make_cor(df7a, vars_intero, with = "mAIA_ATTENTION_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_NOTICING", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NON_DISTRACTING", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7a, vars_intero, with = "MAIA_NOT_WORRYING", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7a, vars_intero, with = "MAIA_EMOTIONAL_AWARENESS", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7a, vars_intero, with = "MAIA_SELF_REGULATION", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7a, vars_intero, with = "MAIA_BODY_LISTENING", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7a, vars_intero, with = "MAIA_TRUSTING", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df7b
  make_cor(df7b, vars_intero, with = "maiaNotice", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df7b, vars_intero, with = "maiaNonDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df7b, vars_intero, with = "maiaNotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df7b, vars_intero, with = "maiaAttentionRegulation", component="MAIA") |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df7b, vars_intero, with = "maiaEmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df7b, vars_intero, with = "maiaSelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df7b, vars_intero, with = "maiaBodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df7b, vars_intero, with = "maiaTrusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting"),

  # df10a
  make_cor(df10a, vars_intero, with = "MAIA_AttentionRegulation", component="MAIA")  |>
    mutate(var_Correlate = "Attention Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_BodyListening", component="MAIA") |>
    mutate(var_Correlate = "Listening"),
  make_cor(df10a, vars_intero, with = "MAIA_EmotionalAwareness", component="MAIA") |>
    mutate(var_Correlate = "Emotional Awareness"),
  make_cor(df10a, vars_intero, with = "MAIA_NotDistracting", component="MAIA") |>
    mutate(var_Correlate = "Not Distracting"),
  make_cor(df10a, vars_intero, with = "MAIA_Noticing", component="MAIA") |>
    mutate(var_Correlate = "Noticing"),
  make_cor(df10a, vars_intero, with = "MAIA_NotWorrying", component="MAIA") |>
    mutate(var_Correlate = "Not Worrying"),
  make_cor(df10a, vars_intero, with = "MAIA_SelfRegulation", component="MAIA") |>
    mutate(var_Correlate = "Self Regulation"),
  make_cor(df10a, vars_intero, with = "MAIA_Trusting", component="MAIA") |>
    mutate(var_Correlate = "Trusting")
)

display_sig(rez_maia)
```

@@

```{r}
# df3$BPQ_BodyAwareness <- -1*normalize(df3$BPQ_BodyAwareness)
# df3$BPQ_AutonomicReactivity <- -1*normalize(df3$BPQ_AutonomicReactivity)
# names(df2)[str_detect(names(df2), "BPQ")]  # BPQ_R_Supra and _Sub?
# names(df3)[str_detect(names(df3), "BPQ")]  
# names(df4)[str_detect(names(df4), "BPQ")]   # individual items 1-26
# names(df7b)[str_detect(names(df7b), "BPQ")]  # BPQ sum
# names(df8a)[str_detect(names(df8a), "BPQ")]  # individual items

df4$BPQ_A <- rowMeans(df4[str_detect(names(df4), "BPQ_")])
df4$BAQ <- rowMeans(df4[,str_detect(names(df4), "BAQ")], na.rm = TRUE)
df4$PBCS <- rowMeans(df4[,str_detect(names(df4), "PBCS")], na.rm = TRUE)
df4$BRS <- rowMeans(df4[,str_detect(names(df4), "BRS")], na.rm = TRUE)
df8a$BPQ_A <- -1*normalize(df8a$BPQ_A)

rez_bpq <- rbind(
  # df2
  make_cor(df2, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df2, vars_intero, with = "BPQ_R", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  make_cor(df2, vars_intero, with = "ICQ", component="Body") |>
    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
  # df3
  make_cor(df3, vars_intero, with = "BPQ_BodyAwareness", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df3, vars_intero, with = "BPQ_AutonomicReactivity", component="Body") |>
    mutate(var_Correlate = "Autonomic Reactivity (BPQ)"),
  # df4
  make_cor(df4, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df4, vars_intero, with = "BAQ", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BAQ)"),
  make_cor(df4, vars_intero, with = "PBCS", component="Body") |>
    mutate(var_Correlate = "Body Consciousness (PBCS)"),
  make_cor(df4, vars_intero, with = "BRS", component="Body") |>
    mutate(var_Correlate = "Body Responsiveness (BRS)"),
  # df 6
  make_cor(df6, vars_intero, with = "IATS_sum", component="Body") |>
    mutate(var_Correlate = "Interoceptive Attention (IATS)"),
  make_cor(df6, vars_intero, with = "SSS8_sum", component="Body") |>
    mutate(var_Correlate = "Somatic Burden (SSS-8)"),
  # df 7b
  make_cor(df7b, vars_intero, with = "BPQ_Sum", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df7b, vars_intero, with = "PHQ15_Sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  # df 7c
  make_cor(df7c, vars_intero, with = "BPQ_sum", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)"),
  make_cor(df7c, vars_intero, with = "ICQ_sum", component="Body") |>
    mutate(var_Correlate = "Interoceptive Confusion (ICQ)"),
  # df8a
  make_cor(df8a, vars_intero, with = "BPQ_A", component="Body") |>
    mutate(var_Correlate = "Body Awareness (BPQ)")
)

display_sig(rez_bpq)
```

### Alexithymia

```{r}
# names(df2)[str_detect(names(df2), "TAS")]
# names(df3)[str_starts(names(df3), "TAS")]
# names(df7c)[str_starts(names(df7c), "TAS")]
# names(df8b)[str_starts(names(df8b), "TAS")]

rez_alexi <- rbind(
  make_cor(df2, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df2, vars_intero, with = "TAS_EOT", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_DescribingFeelings", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_IdentifyingFeelings", component="Alexithymia") |> 
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df3, vars_intero, with = "TAS_ExternallyOrientedThinking", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_des", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ident", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df7c, vars_intero, with = "TAS_ext", component="Alexithymia") |>
    mutate(var_Correlate = "External Thinking (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DIF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Identifying Feelings (TAS)"),
  make_cor(df8b, vars_intero, with = "TAS_DDF", component="Alexithymia") |>
    mutate(var_Correlate = "Difficulties Describing Feelings (TAS)"),
  # BVAQ
  make_cor(df2, vars_intero, with = "BVAQ_Affective", component="Alexithymia") |>
    mutate(var_Correlate = "Affective (BVAQ)"),
  make_cor(df2, vars_intero, with = "BVAQ_Cognitive", component="Alexithymia") |>
    mutate(var_Correlate = "Cognitive (BVAQ)")
)

display_sig(rez_bpq)
```

## Mood

### Depression

```{r}
# names(df6)[str_detect(names(df6), "PHQ")] 
# names(df7b)[str_detect(names(df7b), "PHQ")]
# names(df7c)[str_detect(names(df7c), "BDI")]
# names(df8b)[str_detect(names(df8b), "PHQ")]
# names(df9)

rez_dep <- rbind(
  make_cor(df6, vars_intero, with = "PHQ2_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df7b, vars_intero, with = "PHQ9_Sum", component="Mood")|>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df7c, vars_intero, with = "BDI_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)"),
  make_cor(df8b, vars_intero, with = "PHQ15_sum", component="Mood") |>
    mutate(var_Correlate = "Somatic Concerns (PHQ-15)"),
  make_cor(df8b, vars_intero, with = "PHQ9_sum", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-9)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Depression", component="Mood") |>
    mutate(var_Correlate = "Depression (PHQ-2)"),
  make_cor(df10b, vars_intero, with = "BDI2_Total", component="Mood") |>
    mutate(var_Correlate = "Depression (BDI)")
)

display_sig(rez_dep)
```

### Anxiety

```{r}
# names(df6)[str_detect(names(df6), "GAD")] 
# names(df7a)[str_detect(names(df7a), "STAI")] 
# names(df7b)[str_detect(names(df7b), "STAI")] 
# names(df7c)[str_detect(names(df7c), "STAI")]

rez_anx <- rbind(
  make_cor(df6, vars_intero, with = "GAD2_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df7a, vars_intero, with = "STAI_T_Sumscore", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7b, vars_intero, with = "STAIT_Sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df7c, vars_intero, with = "STAIT_sum", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)"),
  make_cor(df10a, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "PHQ4_Anxiety", component="Mood") |>
    mutate(var_Correlate = "Anxiety (GAD-2)"),
  make_cor(df10b, vars_intero, with = "STAI5_General", component="Mood") |>
    mutate(var_Correlate = "Anxiety (STAI)")
)

display_sig(rez_anx)
```

## Psychopathology

```{r}
rez_bpd <- rbind(
  make_cor(df10a, vars_intero, with = "BPD", component="Mood") |>
    mutate(var_Correlate = "Boderline Personality")
)

display_sig(rez_bpd)
```

```{r}
rez_pid <- rbind(
  make_cor(df10a, vars_intero, with = "PID5_Antagonism", component="Maladaptive") |>
    mutate(var_Correlate = "Antagonism"),
  make_cor(df10a, vars_intero, with = "PID5_Detachment", component="Maladaptive") |>
    mutate(var_Correlate = "Detachment"),
  make_cor(df10a, vars_intero, with = "PID5_Disinhibition", component="Maladaptive") |>
    mutate(var_Correlate = "Disinhibition"),
  make_cor(df10a, vars_intero, with = "PID5_NegativeAffect", component="Maladaptive") |>
    mutate(var_Correlate = "Negative Affect"),
  make_cor(df10a, vars_intero, with = "PID5_Psychoticism", component="Maladaptive") |>
    mutate(var_Correlate = "Psychoticism")
)

display_sig(rez_pid)
```
